%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member of Technical Staff} % Job title
    {PayPal, Inc.} % Organization
    {San Francisco, CA} % Location
    {2018 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to Apple Pay, Venmo, Google Pay, and other wallet products which amounted to ~20\% of transaction volume.}
        \item {Lead Pay with Venmo integrations enabling merchants to accept Venmo as a payment method which grew Venmo processing volume significantly.}
        \item {Lead the transition off of one-time use Discover Cards for Venmo transactions to a closed-loop system enabling faster transaction processing, positive revenue per transaction, and better observability.}
        \item {Enterprise In-Store payments with Verifone P400 POS System enabling touch-less QR Code in-store payments using PayPal and Venmo.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Board Member} % Job title
    {Tufts University, External Advisory Board, Computer Science} % Organization
    {Greater Boston Area} % Location
    {2019-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Advisor on strategic planning to the Tufts Department of Computer Science. Participated in the Diversity, Inclusion, and Belonging committee and advised the department on programs to include underrepresented students in the Computer Science curriculum.}
      \item {The department's mission includes providing top-quality educational experiences for students, advancing the state of knowledge through cutting-edge Computer Science research, and finding solutions to important societal challenges.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Engineering Lead, Purchasing} % Job title
    {Gametime} % Organization
    {San Francisco, CA} % Location
    {2015-2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer for fulfillment and transaction reporting services. Responsible for transactions, mobile APIs, and user/device reporting.}
        \item {Managed direct reports to lower fraud, increase authorization rates, ticket fulfillment rates to lower the burden on customer support teams.}
        \item {Developed automatic fulfillment service to acquire tickets resulting in a 40\% reduction in task time among 2 customer service departments.}
        \item {Lead the technical development of machine vision service to increase ticket fulfillment accuracy by 30\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Gametime} % Organization
    {San Francisco, CA} % Location
    {2014-2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Foundational member of Gametime's full-time engineering team which previously consisted of contractors.}
        \item {Lead the backend development of the first social ticket buying experience in the industry allowing social connections to buy tickets near each other and connect at live events. Applied and received a patent for this feature.}
        \item {Wrote many of the backend functions and REST APIs necessary for customers to buy event tickets in the mobile application, and the delivery system leading to an innovative ticket buying experience.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Rdio} % Organization
    {San Francisco, CA} % Location
    {2012-2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored Android app architecture to use fragments and multiple processes leading to increased playback performance and frame rates.}
        \item {Contributed to a new Data Science and Reporting platform for all the Rdio mobile and web applications, increasing song play reporting accuracy for artist and label payouts. Included both frontend and backend work for app analytics.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
